Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity\vspace{-7ex}

### 2016-08-07 papers/kmeans/kmeans.tex
Clarified heavy/slow neutron-capture, and shut down argument about 'what is an alpha element'

The \apogee\ project shows great promise for these studies, and with
the appearance of the companion papers, we will release the
chemical-abundance measurements we used here for further study.
The future is even brighter, however: \apogee\ is expanding to more measured
elements, more stars, and all-sky angular coverage with \apogee2, and
\galah\ is working towards releasing chemical abundances on a larger set
of 29 elements.
The \apogee\ elements employed in this project include alpha
(Mg, O, Si, S, Ca, Ti), light proton-capture (C, N, S), odd-Z (Na, Al, K)
and iron peak (Fe, Ni, V, Mn) elements.
\galah\ will deliver element abundances from all the major
nucleosynthetic processes, including light proton capture elements,
alpha, odd-Z, iron-peak, light and heavy slow neutron capture, and
rapid neutron capture.
Chemical tagging capabilities are expected to grow as the
\emph{product} of the measured nucleosynthetic pathways.

>>>>

The \apogee\ project shows great promise for these studies, and with
the appearance of the companion papers, we will release the
chemical-abundance measurements we used here for further study.
The future is even brighter, however: \apogee\ is expanding to more measured
elements, more stars, and all-sky angular coverage with \apogee2, and
\galah\ is working towards releasing chemical abundances on a larger set
of 29 elements.
The \apogee\ elements employed in this project include alpha, light proton-capture, odd-Z, and iron peak elements.
\galah\ will deliver element abundances from all the major
nucleosynthetic processes, including light proton capture elements,
alpha, odd-Z, iron-peak, as well as neutron-capture elements.
Chemical tagging capabilities are expected to grow as the
\emph{product} of the measured nucleosynthetic pathways.
